\documentclass{article}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{lipsum}

\begin{document}

\begin{center}
{\fontsize{24}{24}\textbf{Jill Bill's Bakery}}
\end{center}

\vspace{0.5in}

\begin{tabular}{ll}
\textbf{Date:} & March 8, 2025 \\
\textbf{To:} & Beth Harman \\
\textbf{Company:} & Volunteers R Us \\
\textbf{From:} & Jill Bill \\
\textbf{Company:} & Jill Bill's Bakery \\
\textbf{Subject:} & Volunteering at the Bakery \\
\end{tabular}

\vspace{0.5in}

\hrulefill

\vspace{0.5in}

\section*{Introduction}

This document pertains to the volunteering opportunity at Jill Bill's Bakery, offered to and coordinated through Volunteers R Us and Beth Harman. We appreciate your interest in partnering with our bakery and contributing to our community.

\vspace{0.25in}

\section*{Volunteer Activities}

Volunteers participating at Jill Bill's Bakery can expect to engage in a variety of tasks, including:

\begin{itemize}
    \item Assisting with basic food preparation (e.g., measuring ingredients, washing fruits and vegetables).
    \item Packaging baked goods for sale.
    \item Maintaining the cleanliness and organization of the bakery (e.g., sweeping, mopping, wiping down surfaces).
    \item Assisting with customer service, such as greeting customers and helping them find what they need.
    \item Inventory management and stock rotation.
\end{itemize}

\vspace{0.25in}

\section*{Volunteer Guidelines}

All volunteers are expected to adhere to the following guidelines:

\begin{itemize}
    \item Arrive on time for scheduled volunteer shifts.
    \item Dress appropriately (e.g., closed-toe shoes, clean clothing).
    \item Follow instructions from bakery staff.
    \item Maintain a clean and sanitary work environment.
    \item Respect the privacy and confidentiality of customer and employee information.
\end{itemize}

\vspace{0.25in}

\section*{Additional Information}

Please note the following important information:

\begin{itemize}
    \item Volunteer shifts are typically [Number] hours in duration.
    \item Volunteers are provided with a brief orientation upon arrival.
    \item Supervision is provided by designated bakery staff members.
\end{itemize}

\vspace{0.25in}

\section*{Contact Information}

For any questions or concerns, please contact Jill Bill at [Phone Number] or [Email Address].

\vspace{0.25in}

\hrulefill

\vspace{0.5in}

We look forward to welcoming volunteers from Volunteers R Us to Jill Bill's Bakery. Thank you for your support!

\vspace{0.5in}

Sincerely,

Jill Bill

Jill Bill's Bakery

\end{document}